\documentclass[11pt,letterpaper,boxed]{hmcpset}

\usepackage{savetrees}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage[utf8]{inputenc}

\DeclareUnicodeCharacter{2014}{\dash}

\name{Name: \underline{\hspace{5cm}}}
\class{CS159: Natural Language Processing}
\assignment{PReview \#3}
\duedate{Due in class Feb 9, 2015}

\begin{document}

\section*{Review} 
\begin{problem}
Finish the in-class lab. Describe what you found for Parts 3 and
4. Note that Unicode errors are ubiquitous - there was one in the lab
writeup! In Part 4, the title of the document to retrieve should be Château.
\end{problem}

\begin{solution}
\vspace{6cm}
\end{solution}
 
\begin{problem}
For the Wikipedia article of your choice, download and parse both the
English and the Simple English version of the article. You can find
the Simple English version by selecting ``Simple English'' in the list
of languages on the left. Note that not every article has a Simple
English ``translation,'' so you may want to start by finding a good
simple article and then finding the English version. 

Using what you've seen and/or read about in nltk, identify which words
show up more often in the Simple English article and which words show
up more often in the English article relative to the size of the
article. Comment on what, if anything, do you find interesting.
\end{problem}
\begin{solution}
\vspace{6cm}
\end{solution}

\pagebreak

\section*{Preview} 

\begin{problem}
Explain what is meant by the Noisy Channel Model. How does it apply to
machine translation?
\end{problem}
\begin{solution}
\vspace{10cm}
\end{solution}

\begin{problem}
\textbf{MS Exercise 2.4}: Are $X$ and $Y$ as defined in the following
table independently distributed? 
\begin{tabular}{|l|l|l|l|l|}
\hline
$x$ & 0 & 0 & 1 & 1 \\
$y$ & 0 & 1 & 0 & 1 \\
$p(X=x,Y=y)$ & 0.32 & 0.08 & 0.48 & 0.12 \\
\hline
\end{tabular}
\end{problem}
\begin{solution}
\vspace{9cm}
\end{solution}


\end{document}