\documentclass[11pt,letterpaper,boxed]{hmcpset}

\usepackage{savetrees}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{hyperref}

\name{Name: \underline{\hspace{5cm}}}
\class{CS159: Natural Language Processing}
\assignment{PReview \#10}
\duedate{Due in class Apr 20, 2015}

\begin{document}

\section*{Review} 
 
The file \url{http://hmc-cs159-spring2015.github.io/site/handouts/viterbi.py} is partially impelemented for
you. In particular, it uses the nltk brown corpus to build the
transition and observation probabilities for an HMM. The decode()
function is also partially implemented -- it initializes a DP table
and follows back-pointers through the completed DP table to get the
best POS tag sequence. 

Your job is to fill in the actual DP part of the code. 

\begin{problem}

Accoring to your algorithm, what is the most likely tag sequence for
each of the following?

\begin{enumerate}
    \item i see the sheep
    \item the sheep is in the field
    \item who went to the store with you
    \item the plane will land on the land
    \item the horse raced past the barn fell
\end{enumerate}

\end{problem}
\begin{solution}

\begin{enumerate}
    \item \vspace{1cm}
    \item \vspace{1cm}
    \item \vspace{1cm}
    \item \vspace{1cm}
    \item \vspace{1cm}
\end{enumerate}

\end{solution}

\pagebreak

\section*{Preview} 
Five reviews of the movie ``Frozen'' are linked from our course
website: \url{http://hmc-cs159-spring2015.github.io/site/handouts/reviews.pdf}.

\begin{problem}
Based on the reviews, can you predict what rating (on a 1-5 scale)
each reviewer gave the movie? Briefly justify your choice for each.
\end{problem}
\begin{solution}

\begin{description}
    \item {Review 1} \vspace{2cm}
    \item {Review 2} \vspace{2cm}
    \item {Review 3} \vspace{2cm}
    \item {Review 4} \vspace{2cm}
    \item {Review 5} \vspace{2cm}
\end{description}

\end{solution}

\begin{problem}
If you were going to automate the process of predicting scores from
the text, what features might you use? For example, are there specific
words or phrases that are more likely to be associated with positive or
negative reviews? Are there any problems you can foresee with using those features?
\end{problem}
\begin{solution}
\vspace{6cm}
\end{solution}

\end{document}
