\documentclass[11pt,letterpaper,boxed]{hmcpset}

\usepackage{savetrees}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}

\name{Name: \underline{\hspace{5cm}}}
\class{CS159: Natural Language Processing}
\assignment{PReview \#1}
\duedate{Due in class Jan 26, 2015}

\begin{document}

\section*{Review} 
\begin{problem}
Do you have another name you prefer to be called?
\end{problem}

\begin{solution}
\end{solution}

\begin{problem}
Tell me one (or more!) things that you'd like me to know about you.
\end{problem}

\begin{solution}
\vspace{2cm}
\end{solution}

\begin{problem}
What are you most looking forward to getting out of this class?
\end{problem}

\begin{solution}
\vspace{2cm}
\end{solution}

\begin{problem}
What can we do as a class to help you to learn, both in- and out- of
class? What should we avoid doing that would hinder your learning?
\end{problem}

\begin{solution}
\vspace{2cm}
\end{solution}

\pagebreak

\section*{Preview} 
If you will be working on your own machine for this class, follow the
instructions in chapter 1 of the NLTK book to get NLTK installed and
the book datasets downloaded. 

\begin{problem}
What are the first 10 tokens of nltk.book.text6?
\end{problem}

\begin{solution}
\vspace{4cm}
\end{solution}

\begin{problem}
How many times does the word ``nation'' appear in nltk.book.text4?
\end{problem}

\begin{solution}
\end{solution}


\begin{problem}
M\&S Exercise 3.2: Think of five examples of noun-noun compounds.
\end{problem}

\begin{solution}
\vspace{3cm}
\end{solution}

\begin{problem}
M\&S Exercise 3.4: What is the difference in meaning between the
following two sentences?
\begin{enumerate}
    \item  Mary defended her.
    \item Mary defended herself.
\end{enumerate}
\end{problem}

\begin{solution}
\vspace{4cm}
\end{solution}

\end{document}